The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-19 src/static/authors.tex
update Macquarie Univ affiliations
A Department became a School and making other affiliations at Macquarie University consistent.

\author[0000-0001-6637-6922]{James~Tocknell}
\affiliation{Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics - Macquarie, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0003-0353-9741]{Jaime~A.~Alvarado-Montes}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University -- Sydney, NSW 2109, Australia.}
\affiliation{Centre for Astronomy, Astrophysics and Astrophotonics, Macquarie University -- Sydney, NSW 2109, Australia.}

@@

\author{Simon~Conseil}
\affiliation{Univ Lyon, Univ Claude Bernard Lyon 1, CNRS/IN2P3, IP2I Lyon, UMR 5822, F-69622, Villeurbanne, France}

@@

\author[0000-0001-5185-9876]{Lee~R.~Spitler}
\affiliation{Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia}

>>>>

\author[0000-0001-6637-6922]{James~Tocknell}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University -- Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics - Macquarie, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0003-0353-9741]{Jaime~A.~Alvarado-Montes}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University -- Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}

@@

\author[0000-0002-3657-4191]{Simon~Conseil}
\affiliation{Aix Marseille Univ, CNRS, CNES, LAM, Marseille, France}

@@

\author[0000-0001-5185-9876]{Lee~R.~Spitler}
\affiliation{School of Mathematical and Physical Sciences, Macquarie University -- Sydney, NSW 2109, Australia.}
\affiliation{Astronomy, Astrophysics and Astrophotonics Research Centre, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Australian Astronomical Optics - Macquarie, Macquarie University, Sydney, NSW 2109, Australia}
